# Conventions

This book will use the following conventions:

* Generic code: `list(number = 1, letter = "A")`
* Highlighted code: `r hl(dplyr::slice_max())`
* File paths: `r path("data/sales.csv")`
* R Packages: `r pkg("tidyverse")`
* Functions: `r hl(paste())`
* Strings: `r hl("psyTeachR")`
* Numbers: `r hl(100)`, `r hl(3.14)`
* Logical values: `r hl(TRUE)`, `r hl(FALSE)`
* Glossary items: `r glossary("ordinal")`
* Citations: @R-tidyverse
* Internal links: Chapter\ \@ref(inclusion)
* External links: [R for Data Science](https://r4ds.had.co.nz/){target="_blank"}
* Menu/interface options: **`New File...`**

## Webexercises

See [webexercises](https://psyteachr.github.io/webexercises/) for more details about how to use this in your materials.

* Type an integer: `r fitb("^[0-9]{1}$", width = 1, regex = TRUE)`
* I am going to learn a lot: `r mcq(c(answer = "TRUE", x = "FALSE"))`
```{r, echo=FALSE, results='asis'}
# https://psyteachr.github.io/webexercises/
# epub rendering requires all options have a value, so just use x

opts <- c(
   x = "the probability that the null hypothesis is true",
   answer = "the probability of the observed (or more extreme) data, under the assumption that the null-hypothesis is true",
   x = "the probability of making an error in your conclusion"
)
cat("* What is a p-value?", longmcq(opts))
```

```{block, webex.hide="Hidden Text"}
You found some hidden text!
```

```{r, webex.hide="Hidden Code"}
print("You found some hidden code!")
```

## Alert boxes

::: {.info data-latex=""}
Informational asides.
:::

::: {.warning data-latex=""}
Notes to warn you about something.
:::

::: {.dangerous data-latex=""}
Notes about things that could cause serious errors.
:::

::: {.try data-latex=""}
Try it yourself.
:::

## Code Chunks

```{r}
# code chunks
paste("Applied", "Data", "Skills", 1, sep = " ")
```


```{r, eval=FALSE, verbatim='r setup, message = FALSE'}
# code chunks with visible r headers
library(tidyverse)
```

## Glossary

`r glossary::glossary_table()`
