# Glossary

You can use the `glossary()` function to automatically link to a term in the [psyTeachR glossary](https://psyteachr.github.io/glossary/) or make your own project-specific glossary.

This will create a link to the glossary and include a tooltip with a short definition when you hover over the term. Use the following syntax in inline r: `glossary("word")`. For example, common `r glossary("data type", "data types")` are `r glossary("integer")`, `r glossary("double")`, and `r glossary("character")`.

If you need to link to a definition, but are using a different form of the word, add the display version as the second argument (`display`). You can also override the automatic short definition by providing your own in the third argument (`def`). Add the argument `link = FALSE` if you just want the hover definition and not a link to the psyTeachR glossary.

```{r glossary-example, results='asis'}
glossary("data type", 
         display = "Data Types", 
         def = "My custom definition of data types", 
         link = FALSE)
```

You can add a glossary table to the end of a chapter with the following code. It creates a table of all terms used in that chapter previous to the `glossary_table()` function. It uses `kableExtra()`, so if you use it in a code chunk, set `results='asis'`.

```{r, eval=FALSE, verbatim="r, echo=FALSE, results='asis'"} 
glossary_table()
```

`r glossary_table()`

If you want to contribute to the glossary, fork the [github project](https://github.com/PsyTeachR/glossary), add your terms and submit a pull request, or suggest a new term at the [issues page](https://github.com/PsyTeachR/glossary/issues).
